---
title: "PointingXP"
author: "Céline Coutrix"
date: "11/17/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading libraries

```{r loading ggplot2}
library(ggplot2)
```

## Loading data

-   MT = 1001.293 + 140.589 × log(A/W + 1) with R2 = 0.218

```{r loading csv data into a dataframe}
meanMTdf <- read.csv("../data/20211117_1527_MeanMT.csv", header=T)
rawdf <- read.csv("../data/20211117_1527_RawData.csv", header=T)
```

## Loading data new data

-   [experimental software](http://ergo.human.cornell.edu/FittsLaw/FittsLaw.html)
-   w(1,2,4); amp(16,32,64); 6 trial
-   MT = 328.025 + 137.603 × log(A/W + 1) with R2 = 0.604
-   Error: 94

```{r loading csv data into a dataframe}
meanMTdf1 <- read.csv("../data/MeanMT1.csv", header=T)
rawdf1 <- read.csv("../data/RawData1.csv", header=T)
```

## Loading data new data

-   [experimental software](http://ergo.human.cornell.edu/FittsLaw/FittsLaw.html)
-   w(1,2,4); amp(16,32,64); 6 trial
-   MT = 501.167 + 10.220 × log(A/W + 1) with R2 = 0.003
-   Error: 797

```{r loading csv data into a dataframe}
meanMTdf2 <- read.csv("../data/MeanMT2.csv", header=T)
rawdf2 <- read.csv("../data/RawData2.csv", header=T)
```

## Plotting the data together with the linear regression

```{r Plotting the raw data together with the linear regression}
ggplot(meanMTdf, aes(ID, MT, color=A)) +
  geom_point() +
  geom_smooth(method='lm') +
  xlim(1,6) +
  ylim(0, 3000)

ggplot(meanMTdf1, aes(ID, MT, color=A)) +
  geom_point() +
  geom_smooth(method='lm') +
  xlim(1,6) +
  ylim(0, 3000)

ggplot(meanMTdf2, aes(ID, MT, color=A)) +
  geom_point() +
  geom_smooth(method='lm') +
  xlim(1,6) +
  ylim(0, 3000)
```

## Linear modelling

```{r linear modeling}
model <- lm(MT~ID, data = meanMTdf)
summary(model)

model1 <- lm(MT~ID, data = meanMTdf1)
summary(model1)

model2 <- lm(MT~ID, data = meanMTdf2)
summary(model2)
```

Weirdly, in contrast to what Fitts' law says, ID does not seem to have an impact on the movement time. Also, the R2=0.218 reported by the [experimental software](http://ergo.human.cornell.edu/FittsLaw/FittsLaw.html) and the R2=0.008146 I find here, are different.
